Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos

### 2024-10-16 Paper.tex
Update Paper.tex for high-precision spatial-temporal event spotting in volleyball
- Updated the abstract to emphasize the importance of understanding the precise timing and location of events in fast-paced sports like volleyball.
- Removed outdated references to the conference proceedings and retyping requirements.
- Added a new section on related work in the field of action spotting.
- Introduced the new task of high-precision spatial-temporal event spotting in volleyball.
- Described the KOVO Event Dataset, the first dataset with detailed temporal and spatial annotations for volleyball ralli

\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
\affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
\email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
}

@@

% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
\abstract{
  Accurate event spotting in sports videos relies not only on precise temporal detection but also on spatial understanding of key actions within the frame. In volleyball, where fast-paced plays unfold in specific court areas, integrating spatial localization is essential for meaningful analysis. We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, addressing the need to detect both when and where key events occur. To tackle this challenge, we develop a novel volleyball event dataset annotated for both temporal and spatial event localization. Our proposed multi-task deep learning model leverages this dual focus, jointly predicting event timing and spatial coordinates. Remarkably, we find that adding a spatial predictor improves temporal event detection by ???\%, underscoring the synergy between spatial and temporal tasks. Evaluations demonstrate state-of-the-art performance on our dataset, surpassing existing methods in mean Average Precision (mAP), and highlighting the benefits of spatial-temporal networks in sports video analysis.
  }

@@

\section{\uppercase{Introduction}}
\label{sec:introduction}

Your paper will be part of the conference proceedings
therefore we ask that authors follow the guidelines explained in
this example in order to achieve the highest quality possible
\cite{Smith98}.

Be advised that papers in a technically unsuitable form will be
returned for retyping. After returned the manuscript must be
appropriately modified.

@@

\bibliographystyle{apalike}
{\small
\bibliography{example}}

>>>>

\author{\authorname{Hoang Quoc Nguyen\sup{1}\sup{2}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
\affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
\affiliation{\sup{2}University of Science and Technology, Daejeon, Republic of Korea}
\email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
}

@@

\abstract{
  Understanding the precise timing and location of events is crucial for analyzing sports videos, especially in fast-paced sports like volleyball. We introduce a new task: high-precision spatial-temporal event spotting, which aims to detect both when and where key actions occur. To support this, we present the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization. Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds. Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89, underscoring the synergy between spatial and temporal analysis. To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
}

@@

\section{\uppercase{Introduction}}
\label{sec:introduction}
% \section{Introduction}
Video understanding has emerged as a cornerstone in computer vision, offering valuable insights into dynamic scenes for applications such as sports analytics, surveillance, and autonomous systems. Within this field, various tasks have been defined to interpret actions over time. \textit{Temporal Action Detection (TAD)} focuses on pinpointing time intervals where specific actions occur within untrimmed videos, while \textit{Temporal Action Segmentation (TAS)} aims to divide videos into continuous sequences of actions. Complementing these is the task of \textit{Action Spotting}, which zeroes in on identifying the precise frames that capture key events, requiring models to discern subtle temporal differences and visually similar frames \cite{spot22}.

Recent advancements in action spotting, such as \textit{T-DEED} \cite{teed23} and \textit{spot22} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events by leveraging deep learning architectures. However, most of these efforts focus solely on detecting events in specific domains like figure skating and diving. While effective in their respective domains, they do not capture the unique challenges posed by team-based sports with rapid dynamics, such as volleyball.

Despite progress in action spotting, there is a gap in applying these techniques to sports like volleyball, where rapid play transitions occur within specific areas of the court. Addressing this requires a broader focus: \textit{high-precision spatial-temporal event spotting}, a task designed to detect both the exact timing and spatial location of key events. Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, crucial for analyzing volleyball gameplay.

In other sports, datasets like \textit{SoccerNet} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities. Yet, no equivalent dataset exists for volleyball, a sport characterized by its rapid exchanges and the need for precise localization of actions. To fill this gap, we introduce the \textit{KOVO Event Dataset}, comprising 947 rally videos, 890,797 frames, and 5,935 annotated key actions. This dataset offers granular annotations for both temporal and spatial event localization, making it a valuable resource for developing models that capture the intricacies of volleyball.

Our contributions are threefold. First, we introduce the new task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball. Second, we present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies. Third, we propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance. Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points. Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task. To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area. The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.

@@

\bibliographystyle{apalike}
{\small
\bibliography{cite}}
